The following includes additional requirements the the project must have, a more detailed description of each requirement, the source, the constraits, the standards, and finally the priority of each standard that the project must have. Although the team does not have to have a final one hundred percent fully professional project by the deadline which is by the middle of March, the requirements set by TrafficNet must be complete.

\subsection{Requirement}
Some additional requirement would be to arrange all the components of the project into a professional way, cover any logos of components we might use in our project, modularity and extensibility will be required in case future enhancements might be necessary, camera has to be portable, the graphical user interface must be easy to use and work with any type of operating system.
\subsubsection{Description}
The project must be done in a professional manner which means that no hanging cables or messy implementation of components. Modularity and extensibility will be required because in case we decide to add to the project in the future, we want to know exactly what each component and connection does, so that in the future implementation will be easier. The camera does have to be portable, which means that the camera must fit on an enclosed spaced and not be to big or have cables running all over the place. The graphical user interface must be easy to use because we don't want the user to get confused about how to interact with the camera.
\subsubsection{Source}
The source comes from TrafficNet, which they gave us an idea of how the project must be implemented.
\subsubsection{Constraints}
One of the biggest contraints would be for the project to run on not more than 5W of power, which means we must make the project run on very low power and use solar panels to achieve the required amount.
\subsubsection{Standards}
Extreme low power, must have a solar panel and bettery, have pan and tilt capability, heating capability,  easy to use GUI, and 10X zoom.
\subsubsection{Priority}
The top priority would be for the system to run on extreme low power. After the top priority is achieved, the other priorities are as follows, 180 degrees pan and tilt, easy to use GUI, 10X zoom, and finally having a heating capability for extreme weather. 
